Ecological performance of detecting data fabrication with summary statistics

### 2017-03-08 submission/manuscript.Rnw
Sourcing for previous commit
Update study 2 analyses before analyzing for bonus.

# Add ../ before running rmarkdown, or vice versa when not running there
x12 <- '../'
# x12 <- ''
@

@@

<<echo = FALSE>>=
tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[1], ]

>>>>

# Add ../ before running rmarkdown, or vice versa when not running there
x12 <- '../'
# x12 <- ''

source(sprintf('%sfunctions/digit_analysis.R', x12))
source(sprintf('%sfunctions/std_var.R', x12))
@

@@

<<echo = FALSE>>=

df_ml3 <- NULL
# Compute the results for the ML3 data
for(i in 1:length(unique(ml3_dat$study_name)))
{
  tmp <- ml3_dat[ml3_dat$study_name == unique(ml3_dat$study_name)[i], ]

  binder <- data.frame(id = unique(ml3_dat$study_name)[i],
                       benford_congr_m_p = digit_analysis(tmp$MC, type = 'benford')$pval,
                       benford_congr_sd_p = digit_analysis(tmp$SDC, type = 'benford')$pval,
                       benford_incongr_m_p = digit_analysis(tmp$MI, type = 'benford')$pval,
                       benford_incongr_sd_p = digit_analysis(tmp$SDI, type = 'benford')$pval,
                       terminal_congr_m_p = digit_analysis(tmp$MC, type = 'terminal')$pval,
                       terminal_congr_sd_p = digit_analysis(tmp$SDC, type = 'terminal')$pval,
                       terminal_incongr_m_p = digit_analysis(tmp$MI, type = 'terminal')$pval,
                       terminal_incongr_sd_p = digit_analysis(tmp$SDI, type = 'terminal')$pval,
                       std_congr_p = std_var(tmp$SDC, tmp$NC, iter = iter),
                       std_incongr_p = std_var(tmp$SDI, tmp$NI, iter = iter),
                       mult_m_sd_congr = cor(tmp$MC, tmp$SDC),
                       mult_m_sd_incongr = cor(tmp$MI, tmp$SDI),
                       mult_m_m_across = cor(tmp$MC, tmp$MI),
                       mult_sd_sd_across = cor(tmp$SDC, tmp$SDI))

  df_ml3 <- rbind(df_ml3, binder)
}

# The responses from the study
responses <- list.files(sprintf('%sdata/study_02/responses', x12))
df_fab <- NULL

for (response in responses)
{
  fab_dat <- read.table(sprintf('%sdata/study_02/responses/%s', x12, response),
                        sep = '\t', header = TRUE)
  # For clarity sake
  names(fab_dat) <- c('id',
                      'mean_congruent',
                      'sd_congruent',
                      'congruent_trials',
                      'mean_incongruent',
                      'sd_incongruent',
                      'incongruent_trials')

  mult_m_sd_congr <- cor(fab_dat$mean_congruent, fab_dat$sd_congruent)
  mult_m_sd_incongr <- cor(fab_dat$mean_incongruent, fab_dat$sd_incongruent)
  mult_m_m_across <- cor(fab_dat$mean_congruent, fab_dat$mean_incongruent)
  mult_sd_sd_across <- cor(fab_dat$sd_congruent, fab_dat$sd_incongruent)

  p_mult_m_sd_congr <- ifelse(mean(df_ml3$mult_m_sd_congr) > mult_m_sd_congr,
                              sum(df_ml3$mult_m_sd_congr < mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr),
                              sum(df_ml3$mult_m_sd_congr > mult_m_sd_congr) * 2 / length(df_ml3$mult_m_sd_congr))
  p_mult_m_sd_incongr <- ifelse(mean(df_ml3$mult_m_sd_incongr) > mult_m_sd_incongr,
                                sum(df_ml3$mult_m_sd_incongr < mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr),
                                sum(df_ml3$mult_m_sd_incongr > mult_m_sd_incongr) * 2 / length(df_ml3$mult_m_sd_incongr))
  p_mult_m_m_across <- ifelse(mean(df_ml3$mult_m_m_across) > mult_m_m_across,
                              sum(df_ml3$mult_m_m_across < mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across),
                              sum(df_ml3$mult_m_m_across > mult_m_m_across) * 2 / length(df_ml3$mult_m_m_across))
  p_mult_sd_sd_across <- ifelse(mean(df_ml3$mult_sd_sd_across) > mult_sd_sd_across,
                                sum(df_ml3$mult_sd_sd_across < mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across),
                                sum(df_ml3$mult_sd_sd_across > mult_sd_sd_across) * 2 / length(df_ml3$mult_sd_sd_across))

  binder <- data.frame(id = response,
                       benford_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'benford')$pval,
                       benford_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'benford')$pval,
                       benford_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'benford')$pval,
                       benford_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'benford')$pval,
                       terminal_congr_m_p = digit_analysis(fab_dat$mean_congruent, type = 'terminal')$pval,
                       terminal_congr_sd_p = digit_analysis(fab_dat$sd_congruent, type = 'terminal')$pval,
                       terminal_incongr_m_p = digit_analysis(fab_dat$mean_incongruent, type = 'terminal')$pval,
                       terminal_incongr_sd_p = digit_analysis(fab_dat$sd_incongruent, type = 'terminal')$pval,
                       std_congr_p = std_var(fab_dat$sd_congruent, fab_dat$congruent_trials, iter = iter),
                       std_incongr_p = std_var(fab_dat$sd_incongruent, fab_dat$incongruent_trials, iter = iter),
                       p_mult_m_sd_congr,
                       p_mult_m_sd_incongr,
                       p_mult_m_m_across,
                       p_mult_sd_sd_across)

  # Add 1 ten millionth to any zero
  # so the log doesn't go to infinite and messes with the Fisher method
  p_for_fish <- unlist(ifelse(binder[,6:15] == 0, .0000001, binder[,6:15]))

  fish <- -2 * sum(log(p_for_fish))
  df_fish <- length(p_for_fish) * 2
  p_fish <- pchisq(q = fish, df = df_fish, lower.tail = FALSE)
  binder <- cbind(binder, p_fish)

  df_fab <- rbind(df_fab, binder)
}
